Conversas Hiperligadas: Novo Paradigma de Comunicação e Colaboração, potenciado pela Tecnologia WebRTC

### 2016-03-03 curriculo/cv.tex
[ADD] added sample video for testing

\begin{entrylist}
  \entry
    {2015}
    {Bomb Raider}
    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{Google Play}}
    {Bomb Raider is a simple singleplayer and multiplayer game where the goal is destroying all enemies in the map. I used \underline{OpenGLES} and \underline{WiFi-Direct} to develop this \underline{Android} game.}

@@

	My mother said I should have a girlfriend...

@@

\begin{lstlisting}
System.out.println("... but I love programming.");
return 0; // ends gracefully
\end{lstlisting}
\end{document}

>>>>

\begin{entrylist}
  \entry
    {201?}
    {My personal website}
    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{henrique.rocha.pt}}
    {I like PlayFramework, but I still like more to learn different technologies, that's why I did this website using ???, just for fun.}

  \entry
    {2015}
    {Bomb Raider}
    {\href{http://play.google.com/store/apps/details?id=pt.ist.bombraider}{Google Play}}
    {Bomb Raider is a simple singleplayer and multiplayer game where the goal is destroying all enemies in the map. I used \underline{OpenGLES} and \underline{WiFi-Direct} to develop this \underline{Android} game.}

@@

%	My mother said I should have a girlfriend...

@@

\begin{lstlisting}
return 0;
\end{lstlisting}
\end{document}
